\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath}
\usepackage{enumitem}
\title{Fundamental Chemistry Upload Summary}
\date{2026-03-27}
\begin{document}
\maketitle

\section*{Source Scope}
This summary is based on uploaded chemistry worksheet images (Chem 106 / Fundamental Chemistry).

\section*{Core Topics Identified}
\begin{itemize}[leftmargin=*]
  \item \textbf{Intermolecular forces and boiling point}: comparison of molecules with and without hydrogen bonding capability.
  \item \textbf{Heating curves and phase changes}: identifying phase-transition segments and interpreting temperature vs. heat-added graphs.
  \item \textbf{Stoichiometry of rates}: converting between rates of disappearance and appearance using stoichiometric coefficients.
  \item \textbf{Integrated rate laws}: identifying first-order form
  \[
    \ln [A]_t = -kt + \ln [A]_0
  \]
  and graph signatures for zero-, first-, and second-order behavior.
  \item \textbf{Arrhenius relationship}: using slope of $\ln k$ vs. $1/T$ to solve for activation energy
  \[
    \ln k = -\frac{E_a}{R}\left(\frac{1}{T}\right) + \ln A.
  \]
  \item \textbf{Thermodynamics and spontaneity}: using
  \[
    \Delta G = \Delta H - T\Delta S
  \]
  and sign-analysis for spontaneity at low/high temperature.
  \item \textbf{Entropy trends}: predicting sign of $\Delta S$ from particle/phase changes.
  \item \textbf{Colligative properties}: freezing-point depression and boiling-point elevation relationships.
  \item \textbf{Solutions and Henry's law}: gas solubility dependence on partial pressure.
  \item \textbf{Acid/base and electrolyte strength}: distinguishing strong electrolytes from weak electrolytes.
\end{itemize}

\section*{Representative Problem Skills Practiced}
\begin{enumerate}[leftmargin=*]
  \item Select likely weak electrolyte among ionic and molecular species.
  \item Compute boiling-point elevation from solute amount and $K_b$.
  \item Convert gas dissolution data using Henry's constant.
  \item Determine hydrogen-bond donor counts in functionalized molecules.
  \item Identify reaction intermediates from multistep mechanisms.
  \item Relate reaction coordinate diagrams to activation energy and enthalpy change.
\end{enumerate}

\section*{Concise Study Checklist}
\begin{itemize}[leftmargin=*]
  \item Memorize units and interpretation of $\Delta H$, $\Delta S$, and $\Delta G$.
  \item Practice coefficient-based rate conversions until mechanical.
  \item Distinguish integrated rate-law equations by graph linearity.
  \item Rehearse heating-curve segment labeling (warming vs. phase change).
  \item Re-check sign conventions (disappearance rates negative, appearance positive).
\end{itemize}

\end{document}
